---
title: "ggplot plotting functionality"
author: 
   - Markus Lange
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggplot plotting functionality}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---

<style>
.main-container {
  max-width: unset;
}
</style>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dpasurv)
```


## Load data and run analysis

```{r}
data(simdata)

s <- dpa(survival::Surv(start,stop,event)~M+x, list(M~x), id="subject", data=simdata, boot.n=100)

direct <- effect(x ~ outcome, s)
indirect <- effect(x ~ M ~ outcome, s)
total <- sum(direct, indirect)

# Multiple treatment arms:
s2 <- dpa(survival::Surv(start,stop,event)~M+dose, list(M~dose), id="subject", data=simdata, boot.n=100)

direct2 <- effect(dose ~ outcome, s2)
indirect2 <- effect(dose ~ M ~ outcome, s2)
total2 <- sum(direct2, indirect2)
```

## Basic plotting functionality

### Single arm

```{r}
par(mfrow=c(1,3))
plot(direct)
plot(indirect); abline(h=0, lty=2, col=2)
plot(total); abline(h=0, lty=2, col=2)
```

### Multiple arm

```{r, eval=FALSE}
par(mfrow=c(2,3))
plot(direct2); abline(h=0, lty=2, col=2)
plot(indirect2); abline(h=0, lty=2, col=2)
plot(total2); abline(h=0, lty=2, col=2)
```

## ggplot plotting functionality

We can input an object of type "effect"

```{r}
ggplot.effect(indirect)
```

Alternatively, we can provide a list of "effect"-object, for example

```{r}
ggplot.effect(list(direct, indirect, total))
```

Different dose level will be plotted on top of each other

```{r}
ggplot.effect(direct2)
```

Also works when we have multiple treatment arms

```{r}
ggplot.effect(list(direct2, indirect2, total2))
```

It is possible to customize plotting parameters, for example

```{r}
ggplot.effect(list(direct, indirect, total), 
              titles = c("Direct","Indirect","Total"),
              x_label = "Time (in years)", 
              y_label = "Custom y-label")
```

